Alleviating the Topology Mismatch Problem in Unstructured and Structured Overlay Networks: A Survey

### 2014-01-26 unstructured.tex
2012.09.06 (Vassilis) Algorithm depiction reworked.
2012.10.08 (Vassilis) Text added explaining the three indicators (low, medium, high) for each of the criteria against which the algorithms are evaluated (efficiency, overhead, scalability). Filled in missing references and question marks in the tables and text. Intro and background reworked. First page shows the full abstract and bar charts calibrated (orientation, axis labels etc). Text now conforms to ACM Computing Surveys style/format.

\cite{yang_improvep2psearch_2002} proposes an easy to implement and practical
solution to the inefficiency of Gnutella's ``blind flooding'' approach. The
paper introduces three different forwarding methods, namely \emph{iterative
deepening}, \emph{directed BFS}, and \emph{local indices}.

@@

% \begin{center}
% \begin{tabular}{ccc}
% \textbf{Efficiency} & \textbf{Overhead} & \textbf{Scalability} \\
% \hline
% Iterative Deepening & ? & ? & ?
% Directed BFS & ? & ? & ?
% Local Indices & ? & ? & ?
% \end{tabular}
% \end{center}
\begin{center}
\begin{tabular}{rccc}
\multicolumn{1}{r}{} &
\multicolumn{1}{c}{\emph{Efficiency}} &
\multicolumn{1}{c}{\emph{Overhead}} &
\multicolumn{1}{c}{\emph{Scalability}}
\\
\cline{2-4}
\emph{Iterative Deepening} &
% needs recalculation in every iteration step
% extra delay imposed in a high churn environment that prohibits the algorithm
% to start from the last level of nodes and results in a restart of the whole
% process
low &
% the process in not started from the begining at each iteration step
low &
% 
medium \\
\emph{Directed BFS} &
% Better time to satisfaction compared to iterative deepening
medium &
% Better quality and quicker results mean more aggregate bandwidth and
% processing power needs to be consumed since more nodes are involved (death
% spirral).
medium &
% BFS is Gnutella's non efficient communcation method
medium \\
\emph{Local Indices} &
% efficiency is enhanced greatly since data pointers are replicated acros the
% network
high &
% updating indices is a time and resource consuming process.
medium &
% the scalability is constrained by the indices update in a highly dynamic
% environment (high churn)
medium \\
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Gia}
\emph{Gia} \cite{chawathe_gia_2003} is an effort to solve the scalability
problem of the unstructured P2P file sharing systems, in particular Gnutella.
The main novelty in the design of Gia is the replacement of the blind flooding
approach of Gnutella with random walks \cite{lv_randomwalks_2002}. Although
random walks is a step in the right direction, issuing only a single copy of the
query within the network reduces the search scope, thus affecting negatively the
success rate of the query.  In order to overcome this limitation, Gia introduces
a token-based flow control mechanism, which is essentially an intelligent flow
control algorithm that gradually redirects the queries to nodes which are more
likely to answer. In order to prevent overloading of nodes with query requests,
Gia uses a token-based flow control algorithm in which each node announces the
number of query requests it can handle in terms of tokens to its neighbours, so
that neighbours only forward query requests to nodes that they previously
received tokens from. Gia also acknowledges the heterogenity in peer bandwidth,
processing power, disk speed, etc, of the nodes in P2P networks and uses this
information when connecting nodes to each other and by using a topology
adaptation algorithm, Gia ensures that high capacity nodes have high degrees and
low capacity nodes are within short proximity to high capacity ones.
% TODO: THIS FOLLOWING REMARK SOUNDS LIKE THE ALGORITHM SHOULDN'T BE IN THIS
%       SURVEY AFTER ALL!!
Although the topology adaptation algorithm Gia uses improves the scalability of
the network, it does not help much in solving the topology mismatch problem,
since it does not consider the underlying physical topology.

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Drastically reduces the search scope.
low &
% Only one copy of the query is issued to the network.
% A token based flow control mechanism redirects queries to nodes that are most
% likely to fulfill them
low &
% Reduced search scope makes this not really scalable
low
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Distributed Cycle Minimization Protocol (DCMP)}
We have already discussed that blind flooding mechanism broadcasts messages with
no real targeting, many times to a direction far from the path that can
ultimatelly fullfil the query request. Another problem with topology unaware
systems is the duplication of messages due to cycles, even along the correct
forwarding path. The authors of \cite{zhu_dcmp_2008} fucused on that exact
deficiency of overlay networks and introduced Distributed Cycle Minimization
Protocol (DCMP), a dynamic, fully distributed method to remove cycles without
sacrificing overlay connectivity, resilience and other important properties of
unstructured architectures by avoiding a hierarchical organisation of peers. In
DCMP, once a cycle is detected, the most powerful node in that cycle is
elected as the \emph{Gate Peer} and the cycle is then broken at a strategic
place so that it will result in the minimisation of the distance between the
Gate Peer and all other nodes that participated in that cycle. The process
is managed by using two special message types namely \emph{Information
Collection (IC)} and \emph{Cut Message (CM)}. One disadvantage of DCMP is that
since the distance a forwarded message can travel is limited by the TTL value,
which is practically $7$ in most cases DCMP cannot detect cycles formed by more
than 7 peers. Even though cycle elimination improves the network performance, it
does not actually solve the topology mismatch problem.

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% It return more result than LTM according to experiments in
% \cite{zhu_dcmp_2008}
medium &
% Duplicates are an important fraction of the redundant overhead imposed by
% topology mismatch and thus DCMP minimises this as possible.
% The control overhead is also one to two orders of magnitude less than LTM due
% to its ``lazy'' broadcasting of control messages (as opposed to LTM's periodic
% approach) - \cite{zhu_dcmp_2008}
low &
% fully distributed method
high
\end{tabular}
\end{center}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Replication Strategies in Unstructured Peer-to-Peer Networks}
\cite{Cohen02} aim to improve the inefficient blind search algorithm by
replicating the data in a P2P network. The main intuition behind the
idea of replication, or using cached copies, is that as the number of copies for
each item increases in the network, it would be easier for a search algorithm,
even a random one, to locate these items. In order to analyse the feasibility of
such an approach, the authors investigate three different replication
strategies, namely uniform, proportional, and square root allocation. In the
uniform model, the copies of items are uniformly replicated in the network,
while in the proportional model, the items are replicated based on their query
rate, so that frequently queried items are replicated more. The square root
allocation is a strategy proposed in this paper, which is a model between the
uniform and proportional allocation.  In order to evaluate the outcome of the
replication models, the overall costs of successful and unsuccessful searches in
the network are compared. Results argue that the uniform allocation model
minimizes the maximum search size, therefore reduces the time spent on an
unsuccessful search. The proportional model, on the other hand, promotes the
more frequently queried items by replicating them more, therefore decreases the
search time for popular items, but suffers when needing to locate the rare
items. The authors also claim that the expected successful search size is the
same for uniform and proportional models, and any approach between them would
always behave much better. Therefore they propose the square root allocation
approach, which is a replication strategy that minimizes the expected search
size of successful queries in P2P networks.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Tracing a large-scale Peer to Peer System: an hour in the life
of Gnutella}
% TODO: This looks better as an analysis for the unstructured networks in
% general and specifically for caching, so it doesn't seem to contribute any
% new approach.... At least we do not present anything here. Maybe we need to
% revisit the paper itself once more
\cite{Markatos02} analyses Gnutella network traffic traces and by concluding
there is locality among query requests, proposes a caching algorithm that tries
to exploit these findings . The analysis of the trace data reveals other
important facts about the structure of the Gnutella network and the query data.
One significant observation is that the geographic locations of clients do not
have a correlation with the number of query requests they receive. This is an
obvious result of the topology mismatch problem caused by the overlay structure
of the Gnutella network. Gnutella's traffic is observed to be bursty both for
query requests and query responses, even in longer intervals. It is observed
that a peer receives 50 query messages per second on average! Moreover nine out
of ten queries do not generate any response due to the inefficient design of
the Gnutella network. When developing a caching system to exploit locality,
applying an approach similar to web caching does not fit well with P2P systems.
Caches in P2P systems not only have to consider the query string, but also
the TTL value, the source of the query, and the time of the query as well.  In
general, even though optimum caching is hard to achieve, it is reported that
it improves the overall performance of the Gnutella network.

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
%
? &
%
? &
%
?
\end{tabular}
\end{center}

@@

\emph{Narada} \cite{chu_esm_2000,chu_esm_2001,chu_esm_2002} is a generic
protocol for creating self-adapting overlay networks, that can achieve
application-layer multicast communication without requiring IP multicast
infrastructure at the network layer\footnote{
  IP multicast is the term reffering to the method of sending IP datagrams to a
  group of receivers in a single transmission. Even though the method is
  available some years now, IP multicast has not taken off as anticipated since
  many believe that it violates the stateless design of the current Internet.
  For this reason it is widely deployed in contained environments like
  enterprises (i.e. IPTV applications - distance learning, video conferencing),
  commercial stock exchanges, and multimedia content delivery networks.
}. Although it was not originally designed as a P2P system nor can be considered
scalable in the contemporary sense of the term, Narada has been pioneering
(maybe along with \emph{Scattercast} \cite{chawathe_scattercast_2000}) in that
it was the first to consider the feasibility of overlay-based, application
layer, services over the Internet that can take into account bandwidth and
latency properties of the physical underlying infrastructure. Additionally,
authors realised the inefficiency caused by the topology mismatch problem and
tried to encounter it by building a richer connected graph, called a
\emph{mesh}, and building per source minimum spanning trees\footnote{
  ENarada \cite{li_enarada_2008} used Gossip protocol for the construction
}
as shown in Figure~\ref{figure:narada}. They also keep the graph and the trees
dynamically updated while nodes continue to join and leave the network.
Moreover, the protocol tries to ease the physical link stress, the overall
resource usage and the relative delay among end systems. Unfortunately, the most
important limitation of Narada is that although it works reasonably well for
small groups, it does not scale well for larger networks, therefore it is not
suitable for, potentially very large, P2P file sharing application networks.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Adaptive Overlay Topology Optimization (AOTO)}
\emph{Adaptive Overlay Topology Optimization (AOTO)} \cite{liu_aoto_2003} is one
of the first attempts, along with Narada, to address the topology mismatch
problem. AOTO is a distributed algorithm that works in two steps, namelly
\emph{Selective Flooding} and \emph{Active Topology} to optimize the usage of
the underlying physical resourses. In \emph{Selective Flooding} a minimum
spanning tree is built among each peer and its immediate neighbours so that
queries are not flooding the whole network and at the same time without
shrinking the search scope. During \emph{Active Topology}, the overlay
links are revised so that they depict the physical network topology as close as
possible. This is done independently, by each peer by replacing non-flooding
neighbours, with closer nodes. Picking a replacement out of these non-fooding
neighbours follows a random policy (called \emph{Randomized AT} algorithm in the
paper's context). For these steps a peer needs to keep track of communication
costs to all its neighbours (e.g. the network delay) as well as between any
pair of neighbours (meaning also that additional, cost probing, message types
need to be added to the Gnutella protocol). Whenever a new neighbour cost table
is received or there is a change of neighbours, the source peer has to
re-calculate the multicast tree and apply the randomized AT algorithm.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Adaptive Connection Establishment (ACE)}
\emph{Adaptive Connection Establishment (ACE)} \cite{liu_ace_2004} builds an
overlay multicast tree among each source node and the peers within a certain
diameter from the source peer and optimizes the neighbour connections that are
not in that tree. To achieve that it calculates cost between nodes using network
delay as a metric. Each peer probes the costs with its immediate logical
neighbours and forms a \emph{neighbour cost table (NCT)} using a special
routing message type. Two neighbouring peers exchange their NCTs in order for
every peer to obtain the cost between any pair of its local neighbours forming a
small overlay topology. Moreover, based on obtained NCTs a minimum spanning tree
among each peer and its immediate neighbours is built. Ultimately, physically
far away neighbours are replaced by physically close ones. Specifically, a peer
$S$ probes the distance between one of its non-flooding neighbour's neighbour,
say $G$ and $H$ respectively. Assuming that the link to the neighbour's neigbour
($SH$) is smaller that that of the neighbour ($SG$), the later is cut and a new
connection is established. In the oposite situation where $SG$ is smaller than
$SH$ then if $SH$ is smaller that $GH$ then $H$ is preserved as $S$'s new
neighbour. In the case where $SH$ is larger than $SG$ and $GH$, no connection
will be established and $S$ will continue probing another neighbour's neighbour.
The above optimisation is conducted within $1$-neighbour closure (among its
source peer and all its direct neighbours) but the scope can be extended. The
larger the scope, the better topology matching improvement but also the greater
the computational overhead.

@@

%In \emph{Adaptive Connection Establishment (ACE)} \cite{liu_ace_2004}, the
%authors extend the idea of AOTO by introducing optimizations based on the
%depths of the minimum spanning trees. But since the network delay is not
%always a reliable estimation method to detect the physical location of peers,
%the algorithm still suffers from the discrepancies caused by mislocated nodes.

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% compared to LTM it has slow convergence speed.
medium &
% A little bit better that AOTO since the computation here is done within a
% certain diameter from the source peer
high &
% Larger diameter topologies lead to better topology optimization
% rate but also to higher communication and computation overhead.
medium
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Location-aware Topology Matching (LTM)}
\emph{Location-aware Topology Matching (LTM)} \cite{liu_ltm_2004} proposes a
method to optimize the overlay structure of the P2P network based on the
physical topology. To achieve this, peers issue special messages called
\textit{TTL-detector}s with TTL values of 0 and 1 so that the receiving peers
discover one- and two-hop neighbour sets ($N$ and $N^2$ respectively) around
them and calculating communication costs. Calculation is achieved through
timestamp checking, so clocks must be synchronised. The latency information
gathered is later used to evolve the overlay network into a more efficient one,
without reducing the search scope. Each node examines the latency information
among his direct neighbours and those with larger latency are put in to a
will-cut list where they remain for a certain period of time until when they are
ultimatelly cut and recorded to the peer's cut list. Thus, low productive
connections are dropped and replaced by more efficient ones, reducing the
latency on the overall network. Although LTM improves the overall efficiency of
the P2P network, it does not actually use real physical topology information,
just latency metrics, therefore it does not offer a guaranteed safety net for
the topology mismatch problem.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Scalable Bipartite Overlay (SBO)}
\emph{Scalable Bipartite Overlay (SBO)}
\cite{liu_bipartite_IPDPS,liu_bipartite_2007} reduces the overhead of creating
and maintaining a minimum spanning tree cost by randomly dividing the nodes into
two groups, namely red and white and assigning different tasks to different
groups. When a peer joins the network, is randomly assigned with an initial
colour, say red or white (separating all peers into two groups). Then the peer
that plays the role of the bbootstrap host provides the joining peer with a list
of active peers along with their colour information. The later uses this list to
establish connections to differently coloured peers. This way, all peers form a
bipartite overlay. The white peers measure distances to neighbours (red only) by
using the network delay as a metric and report their corresponding red
neighbours. The red peers, equipped with the information of all two-hop
neighbours ($N^2$), creates minimum spanning tree of these neighbours and
assigns efficient forwarding paths. Having a minimum spanning tree with two
hops, a red peer is able to send its queries within that range. Some white
peers, though, have become non-forwarding neighbours. In this phase, such a
(white) neighbour will try to find another red peer being two hops away from its
current red neighbour to replace the later as its new neighbour. The white peers
can further optimize their positions within the overlay if this is required.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Resolving the Topology Mismatch Problem in Unstructured
Peer-to-Peer Networks}
% TODO: to be reviewed

>>>>

\cite{YG-M2002} proposes an easy to implement and practical solution to the
inefficiency of Gnutella's ``blind flooding'' approach. The paper introduces
three different forwarding methods, namely \emph{iterative deepening},
\emph{directed BFS}, and \emph{local indices}.

@@

% \begin{center}
% \begin{tabular}{ccc}
% \textbf{Efficiency} & \textbf{Overhead} & \textbf{Scalability} \\
% \hline
% Iterative Deepening & ? & ? & ?
% Directed BFS & ? & ? & ?
% Local Indices & ? & ? & ?
% \end{tabular}
% \end{center}
\begin{center}
\begin{tabular}{rccc}
\multicolumn{1}{r}{} &
\multicolumn{1}{c}{\emph{Efficiency}} &
\multicolumn{1}{c}{\emph{Overhead}} &
\multicolumn{1}{c}{\emph{Scalability}}
\\
\cline{2-4}
\emph{Iterative Deepening} &
% needs recalculation in every iteration step
% extra delay imposed in a high churn environment that prohibits the algorithm
% to start from the last level of nodes and results in a restart of the whole
% process
low &
% the process in not started from the begining at each iteration step
low &
% 
medium \\
\emph{Directed BFS} &
% Better time to satisfaction compared to iterative deepening
medium &
% Better quality and quicker results mean more aggregate bandwidth and
% processing power needs to be consumed since more nodes are involved (death
% spirral).
medium &
% BFS is Gnutella's non efficient communcation method
medium \\
\emph{Local Indices} &
% efficiency is enhanced greatly since data pointers are replicated across the
% network
high &
% updating indices is a time and resource consuming process.
medium &
% the scalability is constrained by the indices update in a highly dynamic
% environment (high churn)
medium \\
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Gia}
\emph{Gia} \cite{CRBLS2003} is an effort to solve the scalability
problem of the unstructured P2P file sharing systems, in particular Gnutella.
The main novelty in the design of Gia is the replacement of the blind flooding
approach of Gnutella with random walks \cite{lv_randomwalks_2002}. Although
random walks is a step in the right direction, issuing only a single copy of the
query within the network reduces the search scope, thus affecting negatively the
success rate of the query.  In order to overcome this limitation, Gia introduces
a token-based flow control mechanism, which is essentially an intelligent flow
control algorithm that gradually redirects the queries to nodes which are more
likely to answer. In order to prevent overloading of nodes with query requests,
Gia uses a token-based flow control algorithm in which each node announces the
number of query requests it can handle in terms of tokens to its neighbours, so
that neighbours only forward query requests to nodes that they previously
received tokens from. Gia also acknowledges the heterogenity in peer bandwidth,
processing power, disk speed, etc, of the nodes in P2P networks and uses this
information when connecting nodes to each other and by using a topology
adaptation algorithm, Gia ensures that high capacity nodes have high degrees and
low capacity nodes are within short proximity to high capacity ones.
% TODO: THIS FOLLOWING REMARK SOUNDS LIKE THE ALGORITHM SHOULDN'T BE IN THIS
%       SURVEY AFTER ALL!!
Although the topology adaptation algorithm Gia uses improves the scalability of
the network, it does not help much in solving the topology mismatch problem,
since it does not consider the underlying physical topology.

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Drastically reduces the search scope.
low &
% Only one copy of the query is issued to the network.
% A token based flow control mechanism redirects queries to nodes that are most
% likely to fulfill them.
low &
% Even thought the low overhead scalability is reduced by the reducing of
% search scope.
medium
\end{tabular}
\end{center}

% \begin{center}
% \begin{tikzpicture}
% \begin{axis}[
%   ybar,
%    symbolic x coords={
%      Efficiency,
%      Overhead,
%      Scalability
%    },
%    symbolic y coords={lo, med, hi},
%    x tick label style={rotate=45,anchor=east},
%    xtick=data, ytick=data
% ]

% \addplot coordinates {
%   (Efficiency,lo)
%   (Overhead,lo)
%   (Scalability,lo)
% };

% \end{axis}
% \end{tikzpicture}
% \end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Distributed Cycle Minimization Protocol (DCMP)}
We have already discussed that blind flooding mechanism broadcasts messages with
no real targeting, many times to a direction far from the path that can
ultimatelly fullfil the query request. Another problem with topology unaware
systems is the duplication of messages due to cycles, even along the correct
forwarding path. The authors of \cite{ZKB2008} fucused on that exact deficiency
of overlay networks and introduced Distributed Cycle Minimization Protocol
(DCMP), a dynamic, fully distributed method to remove cycles without sacrificing
overlay connectivity, resilience and other important properties of unstructured
architectures by avoiding a hierarchical organisation of peers. In DCMP, once a
cycle is detected, the most powerful node in that cycle is elected as the
\emph{Gate Peer} and the cycle is then broken at a strategic place so that it
will result in the minimisation of the distance between the Gate Peer and all
other nodes that participated in that cycle. The process is managed by using two
special message types namely \emph{Information Collection (IC)} and \emph{Cut
Message (CM)}. One disadvantage of DCMP is that since the distance a forwarded
message can travel is limited by the TTL value, which is practically $7$ in most
cases DCMP cannot detect cycles formed by more than 7 peers. Even though cycle
elimination improves the network performance, it does not actually solve the
topology mismatch problem.

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% It return more result than LTM according to experiments in
% \cite{ZKB2008}
medium &
% Duplicates are an important fraction of the redundant overhead imposed by
% topology mismatch and thus DCMP minimises this as possible.
% The control overhead is also one to two orders of magnitude less than LTM due
% to its ``lazy'' broadcasting of control messages (as opposed to LTM's periodic
% approach) - \cite{ZKB2008}
low &
% fully distributed method
high
\end{tabular}
\end{center}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Replication Strategies in Unstructured Peer-to-Peer Networks}
\cite{CS2002} aim to improve the inefficient blind search algorithm by
replicating the data in a P2P network. The main intuition behind the
idea of replication, or using cached copies, is that as the number of copies for
each item increases in the network, it would be easier for a search algorithm,
even a random one, to locate these items. In order to analyse the feasibility of
such an approach, the authors investigate three different replication
strategies, namely uniform, proportional, and square root allocation. In the
uniform model, the copies of items are uniformly replicated in the network,
while in the proportional model, the items are replicated based on their query
rate, so that frequently queried items are replicated more. The square root
allocation is a strategy proposed in this paper, which is a model between the
uniform and proportional allocation.  In order to evaluate the outcome of the
replication models, the overall costs of successful and unsuccessful searches in
the network are compared. Results argue that the uniform allocation model
minimizes the maximum search size, therefore reduces the time spent on an
unsuccessful search. The proportional model, on the other hand, promotes the
more frequently queried items by replicating them more, therefore decreases the
search time for popular items, but suffers when needing to locate the rare
items. The authors also claim that the expected successful search size is the
same for uniform and proportional models, and any approach between them would
always behave much better. Therefore they propose the square root allocation
approach, which is a replication strategy that minimizes the expected search
size of successful queries in P2P networks.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{Tracing a large-scale Peer to Peer System: an hour in the life
% of Gnutella}
% TODO: This looks better as an analysis for the unstructured networks in
% general and specifically for caching, so it doesn't seem to contribute any
% new approach.... At least we do not present anything here. Maybe we need to
% revisit the paper itself once more
% \cite{Markatos02} analyses Gnutella network traffic traces and by concluding
% there is locality among query requests, proposes a caching algorithm that tries
% to exploit these findings . The analysis of the trace data reveals other
% important facts about the structure of the Gnutella network and the query data.
% One significant observation is that the geographic locations of clients do not
% have a correlation with the number of query requests they receive. This is an
% obvious result of the topology mismatch problem caused by the overlay structure
% of the Gnutella network. Gnutella's traffic is observed to be bursty both for
% query requests and query responses, even in longer intervals. It is observed
% that a peer receives 50 query messages per second on average! Moreover nine out
% of ten queries do not generate any response due to the inefficient design of
% the Gnutella network. When developing a caching system to exploit locality,
% applying an approach similar to web caching does not fit well with P2P systems.
% Caches in P2P systems not only have to consider the query string, but also
% the TTL value, the source of the query, and the time of the query as well.  In
% general, even though optimum caching is hard to achieve, it is reported that
% it improves the overall performance of the Gnutella network.

% \begin{center}
% \begin{tabular}{ccc}
% \emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
% \hline
%
% ? &
%
% ? &
%
% ?
% \end{tabular}
% \end{center}

@@

\emph{Narada} \cite{CRZ2000,CRSZ2001,CRSZ2002} is a generic
protocol for creating self-adapting overlay networks, that can achieve
application-layer multicast communication without requiring IP multicast
infrastructure at the network layer\footnote{
  IP multicast is the term reffering to the method of sending IP datagrams to a
  group of receivers in a single transmission. Even though the method is
  available some years now, IP multicast has not taken off as anticipated since
  many believe that it violates the stateless design of the current Internet.
  For this reason it is widely deployed in contained environments like
  enterprises (i.e. IPTV applications - distance learning, video conferencing),
  commercial stock exchanges, and multimedia content delivery networks.
}. Although it was not originally designed as a P2P system nor can be considered
scalable in the contemporary sense of the term, Narada has been pioneering
(maybe along with \emph{Scattercast} \cite{C2000}) in that
it was the first to consider the feasibility of overlay-based, application
layer, services over the Internet that can take into account bandwidth and
latency properties of the physical underlying infrastructure. Additionally,
authors realised the inefficiency caused by the topology mismatch problem and
tried to encounter it by building a richer connected graph, called a
\emph{mesh}, and building per source minimum spanning trees\footnote{
  ENarada \cite{LYL2008} used Gossip protocol for the
construction
}
as shown in Figure~\ref{figure:narada}. They also keep the graph and the trees
dynamically updated while nodes continue to join and leave the network.
Moreover, the protocol tries to ease the physical link stress, the overall
resource usage and the relative delay among end systems. Unfortunately, the most
important limitation of Narada is that although it works reasonably well for
small groups, it does not scale well for larger networks, therefore it is not
suitable for, potentially very large, P2P file sharing application networks.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Adaptive Overlay Topology Optimization (AOTO)}
\emph{Adaptive Overlay Topology Optimization (AOTO)} \cite{LZXN2003} is one
of the first attempts, along with Narada, to address the topology mismatch
problem. AOTO is a distributed algorithm that works in two steps, namelly
\emph{Selective Flooding} and \emph{Active Topology} to optimize the usage of
the underlying physical resourses. In \emph{Selective Flooding} a minimum
spanning tree is built among each peer and its immediate neighbours so that
queries are not flooding the whole network and at the same time without
shrinking the search scope. During \emph{Active Topology}, the overlay
links are revised so that they depict the physical network topology as close as
possible. This is done independently, by each peer by replacing non-flooding
neighbours, with closer nodes. Picking a replacement out of these non-fooding
neighbours follows a random policy (called \emph{Randomized AT} algorithm in the
paper's context). For these steps a peer needs to keep track of communication
costs to all its neighbours (e.g. the network delay) as well as between any
pair of neighbours (meaning also that additional, cost probing, message types
need to be added to the Gnutella protocol). Whenever a new neighbour cost table
is received or there is a change of neighbours, the source peer has to
re-calculate the multicast tree and apply the randomized AT algorithm.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Adaptive Connection Establishment (ACE)}
\emph{Adaptive Connection Establishment (ACE)} \cite{LZXN2004} builds an
overlay multicast tree among each source node and the peers within a certain
diameter from the source peer and optimizes the neighbour connections that are
not in that tree. To achieve that it calculates cost between nodes using network
delay as a metric. Each peer probes the costs with its immediate logical
neighbours and forms a \emph{neighbour cost table (NCT)} using a special
routing message type. Two neighbouring peers exchange their NCTs in order for
every peer to obtain the cost between any pair of its local neighbours forming a
small overlay topology. Moreover, based on obtained NCTs a minimum spanning tree
among each peer and its immediate neighbours is built. Ultimately, physically
far away neighbours are replaced by physically close ones. Specifically, a peer
$S$ probes the distance between one of its non-flooding neighbour's neighbour,
say $G$ and $H$ respectively. Assuming that the link to the neighbour's neigbour
($SH$) is smaller that that of the neighbour ($SG$), the later is cut and a new
connection is established. In the oposite situation where $SG$ is smaller than
$SH$ then if $SH$ is smaller that $GH$ then $H$ is preserved as $S$'s new
neighbour. In the case where $SH$ is larger than $SG$ and $GH$, no connection
will be established and $S$ will continue probing another neighbour's neighbour.
The above optimisation is conducted within $1$-neighbour closure (among its
source peer and all its direct neighbours) but the scope can be extended. The
larger the scope, the better topology matching improvement but also the greater
the computational overhead.

@@

%In \emph{Adaptive Connection Establishment (ACE)} \cite{LZXN2004}, the
%authors extend the idea of AOTO by introducing optimizations based on the
%depths of the minimum spanning trees. But since the network delay is not
%always a reliable estimation method to detect the physical location of peers,
%the algorithm still suffers from the discrepancies caused by mislocated nodes.

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% compared to LTM it has slow convergence speed.
medium &
% A little bit better that AOTO since the computation here is done within a
% certain diameter from the source peer
medium &
% Larger diameter topologies lead to better topology optimization
% rate but also to higher communication and computation overhead.
medium
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Location-aware Topology Matching (LTM)}
\emph{Location-aware Topology Matching (LTM)} \cite{LLXNZ2004} proposes a
method to optimize the overlay structure of the P2P network based on the
physical topology. To achieve this, peers issue special messages called
\textit{TTL-detector}s with TTL values of 0 and 1 so that the receiving peers
discover one- and two-hop neighbour sets ($N$ and $N^2$ respectively) around
them and calculating communication costs. Calculation is achieved through
timestamp checking, so clocks must be synchronised. The latency information
gathered is later used to evolve the overlay network into a more efficient one,
without reducing the search scope. Each node examines the latency information
among his direct neighbours and those with larger latency are put in to a
will-cut list where they remain for a certain period of time until when they are
ultimatelly cut and recorded to the peer's cut list. Thus, low productive
connections are dropped and replaced by more efficient ones, reducing the
latency on the overall network. Although LTM improves the overall efficiency of
the P2P network, it does not actually use real physical topology information,
just latency metrics, therefore it does not offer a guaranteed safety net for
the topology mismatch problem.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Scalable Bipartite Overlay (SBO)}
\emph{Scalable Bipartite Overlay (SBO)}
\cite{LXN2004,LXN2007} reduces the overhead of creating
and maintaining a minimum spanning tree cost by randomly dividing the nodes into
two groups, namely red and white and assigning different tasks to different
groups. When a peer joins the network, is randomly assigned with an initial
colour, say red or white (separating all peers into two groups). Then the peer
that plays the role of the bbootstrap host provides the joining peer with a list
of active peers along with their colour information. The later uses this list to
establish connections to differently coloured peers. This way, all peers form a
bipartite overlay. The white peers measure distances to neighbours (red only) by
using the network delay as a metric and report their corresponding red
neighbours. The red peers, equipped with the information of all two-hop
neighbours ($N^2$), creates minimum spanning tree of these neighbours and
assigns efficient forwarding paths. Having a minimum spanning tree with two
hops, a red peer is able to send its queries within that range. Some white
peers, though, have become non-forwarding neighbours. In this phase, such a
(white) neighbour will try to find another red peer being two hops away from its
current red neighbour to replace the later as its new neighbour. The white peers
can further optimize their positions within the overlay if this is required.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{Resolving the Topology Mismatch Problem in Unstructured
% Peer-to-Peer Networks}
% TODO: to be reviewed
